Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-04 Paper/results.tex
Update paper

The comparison of the wind spectra and maximum resolvable frequency
$f_{max}$ for the different mesh resolutions is shown in figure
\ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20 m
height and averaged using 1/3 octave-bins to enhance clarity. For the
$S_u$ and $S_w$ spectra, there are noticeable shifts in the peak
amplitude, while the peak amplitudes for $S_v$ remained fairly
constant between cases.  In all cases, the peak frequency of $S_i(f)$
also increased as the resolution increased. While the mesh resolution
was sufficient to capture the peak frequency for $S_u$, the fine
resolution with 2.5m mesh cells was required to capture the spectral
peaks in the lateral and vertical directions.
\fxnote{OK for temporal resolution}

The second metric for determining the appropriate grid size and mesh
resolution is through the correlation tensor and turbulence integral
length scale.  The two-point correlation tensor
$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at position $\mathbf{x}$ and
separation vector $\boldsymbol{\xi}$ is defined as
\begin{equation}
  \label{eq:Rij}
  R_{ij}({\mathbf x},\boldsymbol{\xi}) =
  \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
\end{equation}
where the velocity fluctuations $u'_i$ are defined as
\begin{equation}
  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
\end{equation}
and the overbar operator $\overline{(\bullet)}$ denotes time
averaging.  In the current study, we compute the horizontally averaged
correlation coefficient $\langle R_{11}(\boldsymbol{\xi})\rangle$ by
sampling over multiple points at the $z$=20 m height, typically 100-150
points, and averaging the result.  The longitudinal $\langle
R_{11}(\boldsymbol{\xi})\rangle$ was calculated by looking at
separation vectors $\boldsymbol{\xi}$ in the streamwise direction
while the lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$ used
separation distances $\boldsymbol{\xi}$ which were orthogonal to the
wind direction on the same horizontal plane.

@@

%%%%%%%%%%% z=20 m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \begin{tikzpicture}
    % 5 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,4.50in)
         {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 4.50in){(a) horizontal vel, 5 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
         {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 4.50in){(b) vertical vel, 5 m/s};

    % 10 m/s plots    
    \node[anchor=south west, inner sep=0](image) at (0in,2.25in)
         {\includegraphics[width=3in]{figures/snapshots/10ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 2.25in){(c) horizontal vel, 10 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,2.10in)
         {\includegraphics[width=3.20in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 2.25in){(d) vertical vel, 10 m/s};

    % 15 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,0in)
         {\includegraphics[width=3in]{figures/snapshots/15ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 0in){(e) horizontal vel, 15 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,-0.15in)
         {\includegraphics[width=3.20in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 0in){(f) vertical vel, 15 m/s};

>>>>

The comparison of the wind spectra and maximum resolvable frequency
$f_{max}$ for the different mesh resolutions is shown in figure
\ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20 m
height and averaged using 1/3 octave-bins to enhance clarity. For the
$S_u$ and $S_w$ spectra, there are noticeable shifts in the peak
amplitude, while the peak amplitudes for $S_v$ remained fairly
constant between cases.  In all cases, the peak frequency of $S_i(f)$
also increased as the resolution increased. While the mesh resolution
was sufficient to capture the peak frequency for $S_u$, the fine
resolution with 2.5m mesh cells was required to capture the spectral
peaks for the lateral and vertical velocities.

However, the above analysis of spectra only provides information to
determine if the turbulent fluctuations can be resolved temporally,
and a separate analysis is needed to determine if the fluctuations can
be resolved in different spatial directions.  The second metric for
examining the appropriate grid size and mesh resolution is through the
correlation tensor and turbulence integral length scale.  The
two-point correlation tensor $R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at
position $\mathbf{x}$ and separation vector $\boldsymbol{\xi}$ is
defined as
\begin{equation}
  \label{eq:Rij}
  R_{ij}({\mathbf x},\boldsymbol{\xi}) =
  \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
\end{equation}
where the velocity fluctuations $u'_i$ are defined as
\begin{equation}
  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
\end{equation}
and the overbar operator $\overline{(\bullet)}$ denotes time
averaging.  In the current study, we compute the horizontally averaged
correlation coefficient $\langle R_{11}(\boldsymbol{\xi})\rangle$ by
sampling over multiple points at the $z$=20 m height, typically 100-150
points, and averaging the result.  The longitudinal $\langle
R_{11}(\boldsymbol{\xi})\rangle$ was calculated by looking at
separation vectors $\boldsymbol{\xi}$ in the streamwise direction
while the lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$ used
separation distances $\boldsymbol{\xi}$ which were orthogonal to the
wind direction on the same horizontal plane.

@@

%%%%%%%%%%% z=20 m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \begin{tikzpicture}
    % 5 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,4.50in)
         {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 4.50in){(a) horizontal vel., stable 5 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
         {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 4.50in){(b) vertical vel., stable 5 m/s};

    % 10 m/s plots    
    \node[anchor=south west, inner sep=0](image) at (0in,2.25in)
         {\includegraphics[width=3in]{figures/snapshots/10ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 2.25in){(c) horizontal vel., stable 10 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,2.10in)
         {\includegraphics[width=3.20in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 2.25in){(d) vertical vel., stable 10 m/s};

    % 15 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,0in)
         {\includegraphics[width=3in]{figures/snapshots/15ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 0in){(e) horizontal vel., stable 15 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,-0.15in)
         {\includegraphics[width=3.20in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 0in){(f) vertical vel., stable 15 m/s};
